---
title: "lab6AdvR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lab6AdvR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Lab6AdvR)
```

first i have define the dataframe here which i am gonna use later.

```{r echo=TRUE}
RNGversion(min(as.character(getRversion()),"3.5.3"))
set.seed(42, kind = "Mersenne-Twister", normal.kind = "Inversion")
n <- 2000
knapsack_objects <-
  data.frame(
    w=sample(1:4000, size = n, replace = TRUE),
    v=runif(n = n, 0, 10000)
  )

```
Tested on Mac, using 8/2 = 4 cores. Machine had 8 cores in total.

```{r }
"Using (parallel= TRUE): 0.007"
"Using (parallel= FALSE): 0.014"

```

What performance gain could you get by parallelizing brute force search?
```{r }
"Almost 2x increase in speed: (0.014/0.007 = 2)"
```

```{r }
brute_force_knapsack(x = knapsack_objects[1:8,], W = 3500)

```

How much time does it takes to run the algorithm for n = 16 objects?
```{r }
 "using 2 cores on Mac"
 "parallel=FALSE => 0.013"
 "parallel=TRUE => 0.488"
```


here we have to run the Greedy Knapsack Algorithm.

```{r }
greedy_knapsack(x = knapsack_objects[1:1200,], W = 3500)
```

How much time does it takes to run the algorithm for n = 500 objects?
```{r }
 "time taken - 0.2 sec"
```


here we have to run the Dynamic Knapsack Algorithm.

```{r }
dynamic_knapsack(x = knapsack_objects[1:12,], W = 1500)

```


How much time does it takes to run the algorithm for n = 1000000 objects?
```{r }
 "time taken - 0.02765918 sec"
```


### What performance gain could you get by trying to improving your code?
In bruit force algorithem implementation i identify the bottle neck of my inplemetation i.e. lapply finction and using combn inside of it. This bottleneck was not resolved since it was already according to our best logic. Other than that there was no bottleneck in our code.

In Dynamic Knapsack, we identified the bottleneck a loop. There was an if condition that was being used in the while loop and was running n times. We replaced the if condition with the branchless coding so that it does not have to waste cpu cycles checking for the if condition . This improved our speed for about 11%.

```{r echo=FALSE}
        'matrixx[Columss, Rowss] <- max(matrixx[Columss - 1, Rowss], matrixx[Columss - 1, Rowss - x[["w"]][Columss]] + x[["v"]][Columss])'
```

In greedy, we saw in profiling that the maximum time was taken inside the for loop. But this bottleneck could not be released. 

Commands used in profiling:
```{r echo=FALSE}
  'l= lineprof(brute_force_knapsack(x = knapsack_objects[1:500,],W=3500))'
  'shine (l)'
```

