---
title: "lab6AdvR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lab6AdvR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Lab6AdvR)
```

first i have define the dataframe here which i am gonna use later.

```{r echo=TRUE}
RNGversion(min(as.character(getRversion()),"3.5.3"))
set.seed(42, kind = "Mersenne-Twister", normal.kind = "Inversion")
n <- 2000
knapsack_objects <-
  data.frame(
    w=sample(1:4000, size = n, replace = TRUE),
    v=runif(n = n, 0, 10000)
  )

```

here we have to run the Bruitforce Knapsack Algorithm.

```{r }
brute_force_knapsack(x = knapsack_objects[1:8,], W = 3500)

```

How much time does it takes to run the algorithm for n = 16 objects?
```{r }
 "using 2 cores on Mac"
 "parallel=FALSE => 0.013"
 "parallel=TRUE => 0.488"
```


here we have to run the Greedy Knapsack Algorithm.

```{r }
greedy_knapsack(x = knapsack_objects[1:1200,], W = 3500)
```

How much time does it takes to run the algorithm for n = 500 objects?
```{r }
 "time taken - 0.2 sec"
```


here we have to run the Dynamic Knapsack Algorithm.

```{r }
dynamic_knapsack(x = knapsack_objects[1:12,], W = 1500)

```


How much time does it takes to run the algorithm for n = 1000000 objects?
```{r }
 "time taken - 0.02765918 sec"
```
